---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# noswimming

<!-- badges: start -->
<!-- badges: end -->

The goal of noswimming is to prevent animals from leaving the ocean. (i.e. no swimming on land is allowed)

## WIP

The name isn't very serious, or accurate, or what we want. TBD 

## Installation

You can install the development version of noswimming like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which finds the least cost path around land (we get a topographic dataset under the hood to figure this out). 

```{r example}
library(noswimming)
#pt <- cbind(c(-90, 90), c(-70, -60))
pt <- cbind(c(138, 153),  c(-36, -23))
path <- lcp(pt)

library(terra)
## we get the data in the projection use
plot(path)
## so reproject for longlat use
plot(terra::project(path, "EPSG:4326"), lty = 2, col = "firebrick")
maps::map(add = TRUE)
```

We can also obtain the intermediate datasets used in the above process. 

```{r intermediate}

topo <- make_global_topo(pt)

## here we might customize the min and max value of the topography (from [-Inf,0])
surf <- make_na_surface(topo)

path <- lcp(pt, surf = surf)
```

## Code of Conduct
  
Please note that the noswimming project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
